---
title: "Assignment02"
author: "Ken Suzuki"
date: "2023-11-21"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For this assignment, you will be using the sat.act dataset available within the psych package in R.
```{r}
library(psych)
d <- sat.act 
head(d)
str(d)
```

### Variables
```
1) Gender: 1 = males; 2 = females
2) Education: 0 = less than high school; 1 = high school; 2 = post-secondary diploma program; 3 = some university/college; 4 = completed university/college; 5 = graduate work.
3) Age = age in years
4) ACT = American College Test (ranges from 0 to 36)
5) SATQ = Standard Aptitude Test – Quantitative (ranges from 200-800)
6) SATV = Standard Aptitude Test – Verbal (ranges from 200-800)
```
**For the questions below, use α = .10 for any null hypothesis significance tests.**

### Part A (12 marks)
Explore how the interaction between gender and age affects scores on the SATQ. More specifically,summarize the findings related to this effect, including the following:

1) Set-up the variables/model and print the results (3 marks)
```{r}
# Set up the linear model in the interaction term between gender and age
model01 <- lm(SATQ ~ gender * age, data = d)
confint(model01, level = 0.90)
summary(model01)
```
2) Summarize the traditional null hypothesis significance testing results (1 mark)

**Gender**  
The coefficient estimate of gender is 0.1320, indicating a potential increase of 0.1320 units in the SATQ score when gender changes from male to female, holding all other variables constant. However, this finding is not statistically significant as the p-value, 0.9960, exceeds the a = 0.10. This notion is also evident as the Confidence Interval ranges from -42.7283407 to 42.992317966 that includes zero within its range. 

**Age**  
The coefficient estimate of age is 2.0769, indicating that one-unit increase in the age is potentially associated with an increase by 2.0769 points in SATQ when other variables are controlled for. However, p-value exceeds the alpha level of 0.1 and this association is not statistically significant. Confidence interval ranges between -0.5654472 and 4.719193133, which zero is included in the range, implying that the effect may not significant.

**Interaction Term between Gender and Age**  
The coefficient estimate of the interaction term of age and gender is -1.5611, indicating that one year increase in age has a potential decrease in SATQ score between male and female by 1.5611. The corresponding p-value 0.0996 is statistically significant when alpha = .10.  

3) Plot the interaction, with a summary of visualization (2 marks)
4) Conduct a negligible effect test on the interaction (using a negligible effect interval of b = -2 to b = 2), and summarize the results (3 marks)

Note that specifying the formula with the following formats will not work in neg.reg: y ~x1*x2 or y ~ x1 + x2 + x1:x2. There are two ways around this: a) compute the interaction term before running the model (e.g., int = x1*x2, using a numeric version of gender), and then use neg.reg (formula = y ~ x1 + x2 + int), or b) compute the confidence intervalfor the interaction separately using confint(model).
```

5) Provide an interpretation of the magnitude of the interaction using both standardized and
unstandardized units, as well as an interpretation of magnitude using the proportional
distance (specific to the negligible effect test). (3 marks)