---
title: "Assignment02"
author: "Ken Suzuki"
date: "2023-11-21"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For this assignment, you will be using the sat.act dataset available within the psych package in R.
```{r}
library(psych)
d <- sat.act 
head(d)
str(d)
```

### Variables
```
1) Gender: 1 = males; 2 = females
2) Education: 0 = less than high school; 1 = high school; 2 = post-secondary diploma program; 3 = some university/college; 4 = completed university/college; 5 = graduate work.
3) Age = age in years
4) ACT = American College Test (ranges from 0 to 36)
5) SATQ = Standard Aptitude Test – Quantitative (ranges from 200-800)
6) SATV = Standard Aptitude Test – Verbal (ranges from 200-800)
```
For the questions below, use α = .10 for any null hypothesis significance tests.

### Part A (12 marks)
Explore how the interaction between gender and age affects scores on the SATQ. More specifically,summarize the findings related to this effect, including the following:

1) Set-up the variables/model and print the results (3 marks)
```{r}
model01 <- lm(SATQ ~ gender * age, data = d)
confint(model01, level = 0.90)
summary(model01)
```


2) Summarize the traditional null hypothesis significance testing results (1 mark)
3) Plot the interaction, with a summary of visualization (2 marks)
4) Conduct a negligible effect test on the interaction (using a negligible effect interval of b = -2 to b = 2), and summarize the results (3 marks)
```
Note that specifying the formula with the following formats will not work in neg.reg: y ~x1*x2 or y ~ x1 + x2 + x1:x2. There are two ways around this: a) compute the interaction term before running the model (e.g., int = x1*x2, using a numeric version of gender), and then use neg.reg (formula = y ~ x1 + x2 + int), or b) compute the confidence intervalfor the interaction separately using confint(model).
```

5) Provide an interpretation of the magnitude of the interaction using both standardized and
unstandardized units, as well as an interpretation of magnitude using the proportional
distance (specific to the negligible effect test). (3 marks)