---
title: "Assignment02"
author: "Ken Suzuki"
date: "2023-11-21"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For this assignment, you will be using the sat.act dataset available within the psych package in R.
```{r}
library(psych)
library(tidyverse)
library(mice)
d <- sat.act 
head(d)
str(d)

# Data Preparation
d$ACT <- as.numeric(d$ACT)
d$SATV <- as.numeric(d$SATV)
d$SATQ <- as.numeric(d$SATQ)

d_gender <- d %>%
  mutate(gender = case_when(
    gender == 1 ~ "male",
    gender == 2 ~ "female"
  ))

# Find if there are any NAs in the data.
any(is.na(d_gender))

# Imputation (used norm.predict)
?mice
imp_d <- mice(d_gender, m = 10, method = "norm.nob", seed = 123)
d02 <- complete(imp_d)

any(is.na(d02))
```

### Variables
```
1) Gender: 1 = males; 2 = females
2) Education: 0 = less than high school; 1 = high school; 2 = post-secondary diploma program; 3 = some university/college; 4 = completed university/college; 5 = graduate work.
3) Age = age in years
4) ACT = American College Test (ranges from 0 to 36)
5) SATQ = Standard Aptitude Test – Quantitative (ranges from 200-800)
6) SATV = Standard Aptitude Test – Verbal (ranges from 200-800)
```
**For the questions below, use α = .10 for any null hypothesis significance tests.**

### Part A (12 marks)
Explore how the interaction between gender and age affects scores on the SATQ. More specifically,summarize the findings related to this effect, including the following:

1) Set-up the variables/model and print the results (3 marks)
```{r}
# Set up the linear model in the interaction term between gender and age for SATQ score.
model01 <- lm(SATQ ~ gender * age, data = d02)
summary(d02)
confint(model01, level = 0.90)
summary(model01)
```
2) Summarize the traditional null hypothesis significance testing results (1 mark)

**Gender**  
The coefficient estimate of gender is -2.8073, indicating a potential decrease of 2.8073 points in the SATQ score when gender changes from male to female, holding all other variables constant. However, this finding is not statistically significant as the p-value, 0.9136, exceeds the a = 0.10 threshold. This notion is also supported by the Confidence Interval, which includes zero in its ranges of -45.42246401 to 39.80795978. 

**Age**  
The coefficient estimate of age is -0.9927, indicating that for one-year increase in the age is potentially associated with an decrease by 0.9927 points in SATQ when all other variables are controlled for. The corresponding p-value is 0.0840 and less than the alpha level threshold of 0.1. Therefore, this estimate is statistically significant. Confidence interval ranges between -1.93767763 and -0.04772478, also suggesting that the effect might be statistically significant.

**Interaction Term between Gender and Age**  
The coefficient of 1.5978 for the interaction term suggests that the impact of age on SATQ scores is different for males compared to females. More specifically, for each additional year, the SATQ score for males is expected to increase by 1.5978 points more than it would for females, holding all other predictors constant.The corresponding p-value 0.0996 is statistically significant when alpha = .10. The confidence interval ranges from 0.04478906   3.15086977, which also suggests that there is an interaction.

**Residual SE**
SATQ score ranges from 200 - 828.6, and RSE is 114.3 on 696 degrees of freedom, I consider RSE not outrageiously large. Therefore, the model has a reasonable hit.

**Adjusted R^2**
Adjusted R^2 was 0.02566 suggesting that the only 2.566% of the variance in SATQ is explained by this model, suggesting that there are other variables that may be in play in changing SATQ scores.

**F-statistic**
F-value of 7.136 on 3 and 696 defgree of freedom draws the p-value of 0.0001. This very small p-value challenges the null hypothesis and suggests that changes in SATQ scores are influenced by age, gender and their interaction.


3) Plot the interaction, with a summary of visualization (2 marks)
```{r}
library(ggplot2)
ggplot(data = d02, aes(x = age, y = SATQ, colour = gender)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SATQ Score by Age and Gender",
       x = "Age",
       y = "SATQ Score") +
  theme_minimal()
```

4) Conduct a negligible effect test on the interaction (using a negligible effect interval of b = -2 to b = 2), and summarize the results (3 marks)
```
Note that specifying the formula with the following formats will not work in neg.reg: y ~x1*x2 or y ~ x1 + x2 + x1:x2. There are two ways around this: a) compute the interaction term before running the model (e.g., int = x1*x2, using a numeric version of gender), and then use neg.reg (formula = y ~ x1 + x2 + int), or b) compute the confidence interval for the interaction separately using confint(model).
```
```{r}
# Mutate gender back to numeric using imputated data d02
d03 <- d02 %>%
  mutate(gender = case_when(
    gender == "male" ~ 1,
    gender == "female" ~ 2
  ))
str(d03)

# Add an interaction term in the dataset
d03$interaction <- d03$gender * d03$age

library(negligible)
# Unstandardized std - FALSE (Default)
neg.reg(formula = SATQ ~ age + gender + interaction, test = "TOST", data = d03, predictor = interaction, eil = -2, eiu = 2)

# Standardized
neg.reg(formula = SATQ ~ age + gender + interaction, test = "TOST", data = d03, predictor = interaction, eil = -2, eiu = 2, std = TRUE)

```
The interaction term (age * gender) has a negative slope of b = -1.598. This implies that one unit increase in the interaction term 
b = -1.598, 90% CI [-3.072, -0.058]
std. error = 0.943


5) Provide an interpretation of the magnitude of the interaction using both standardized and
unstandardized units, as well as an interpretation of magnitude using the proportional
distance (specific to the negligible effect test). (3 marks)